---
title: "stat Project"
author: "Praveen Kumar"
date: "02/05/2022"
output: html_document
---
```{r}
library(ggplot2)
library(metan)
library(dplyr)
library(ggcorrplot)
library(corrplot)
```

Now a  days highly common travelling with airlines companies and since it is common.
Customer satisfication is one of the most important deciding factor.


```{r}
plane <- read.csv(file.choose(),header=TRUE)
```

                                      Problem Definition
                                      
        Customer satisfaction survey we can predict the most essential feature that leads to satisfied customer they are seat comfort     checkin service etc....
        Then, we can predict the rating of the passenger we can predict which featured are important and which should be improved..
        
        
                                      General information about the Datasset 
                                      
        This dataset is US Airline passenger satisfaction survey
        Dataset is obtained from kaggle 
        there are 24 features and 129880 observations
        There are two classes called "satisfied" and "Netural/ Dissatisfied"
        
        
        Key variables
            Satisfaction
            grnder
            age
            customer type
            travel time
            flight distance
```{r}
head(plane)
```

```{r}
tail(plane)
```

```{r}
dim(plane)
```

```{r}
colnames(plane)
```

```{r}
summary(plane)
```
```{r}
sum(is.na(plane))
```

```{r}
sapply(plane,function(X) sum(is.na(X)))
```

```{r}
hist(plane$Arrival.Delay, xlab = "A journey makes lately", col= "blue",main = "Arrival delay",xlim = c(0,400), breaks = 50 )
```

```{r}
plane$Arrival.Delay[is.na(plane$Arrival.Delay)] <- median(plane$Arrival.Delay, na.rm = TRUE)
sum(is.na(plane))
```

```{r}
sapply(plane,function(X) sum(is.na(X)))
```

```{r}
plane$Gender= factor(plane$Gender,
                     levels = c('Female','Male'),
                     labels = c(0,1))
```


```{r}
ggplot(plane, aes(Satisfaction)) + geom_bar()
```

```{r}
table(plane$Satisfaction)
```

```{r}
ggplot(plane, aes(x = Gender )) + geom_bar(aes(fill=Satisfaction), position = "dodge")

```

```{r}
table(plane$Gender)
```
```{r}
ggplot(plane, aes(x= Type_of_Travel)) + geom_bar(aes(fill=Satisfaction), position = "dodge")
```

```{r}
ggplot(plane, aes(x= Class)) + geom_bar(aes(fill=Satisfaction),position = "dodge")                                                        
```



```{r}
ggplot(plane,aes(Customer.Type,..count..)) + geom_bar(aes(fill=Satisfaction), position = "dodge")
```

```{r}
 ggplot(plane, aes(x=Flight.Distance))+
      geom_histogram(fill="#619cff")+
  
      labs(y="", x="flight distance")
```


```{r}
ggplot(plane, aes(x=Departure.Delay))+
                geom_histogram(fill="#619cff")+
                xlim(0,250)+ylim(0,15000)+
                labs(x="departure delay (mins)")
```

```{r}
ggplot(plane, aes(x=Arrival.Delay))+
  geom_histogram(fill="#619cff")+
  xlim(0,250)+ylim(0,15000)+
  labs(y="", x="arrival delay (mins)")

```
```{r}
colnames(plane)
```

```{r}
ggplot(plane, aes(x= Seat.Comfort,..count..)) + geom_bar(aes(fill= Satisfaction),position = "dodge")

ggplot(plane, aes(x= Online.Boarding,..count..)) + geom_bar(aes(fill= Satisfaction),position = "dodge")

ggplot(plane, aes(x= Cleanliness,..count..)) + geom_bar(aes(fill= Satisfaction),position = "dodge")

ggplot(plane, aes(x= In.flight.Entertainment,..count..)) + geom_bar(aes(fill= Satisfaction),position = "dodge")

ggplot(plane, aes(x= Check.in.Service,..count..)) + geom_bar(aes(fill= Satisfaction),position = "dodge")

```



```{r}
df_test<-plane
df_test$Satisfaction<-dplyr::recode(plane$Satisfaction, 'neutral or dissatisfied' = 0, 'satisfied' = 1)
num_df<-df_test %>% select_if(is.numeric)
cor_matrix<-cor(num_df)

ggcorrplot(cor_matrix)+
  theme_classic()+ scale_x_discrete(expand=c(0,0)) +
 scale_y_discrete(expand=c(0,0)) 
```


```{r}
correl <- corr_coef(plane,width_greater_than(9))
plot(correl)
```

```{r}
corr_plot(plane)
```

```{r}
install.packages("corrplot")
```



```{r}
inspect(plane,Arrival.Delay, Departure.Delay, plot = TRUE )
```

```{r}
find_outliers(plane, Arrival.Delay, plots = TRUE)
```

```{r}
corrplot(cor(plane), addCoef.col = 'white',
number.cex = 0.8,
number.digits = 1,
diag = FALSE,
bg = 'grey',
outline = "black",
addgrid.col = "white",
mar = c(1,1,1,1))
```



















                Insights
                    Increasing a Wifi quality
                    On-board service
                    Online boarding
                    marketing to the Business segment